### 2023-06-30 journal/related.tex
Added discussion of Dodds Haas and Kirsch's queue.

>>>>

Dodds, Haas and Kirsch described how a queue could be implemented similarly
to their lock-free stack \cite{DHK15}.  To enqueue an item, a process adds the item, together with an associated timestamp,
to the process's own single-enqueuer multi-dequeuer queue, which is implemented as a linked list.  
Although enqueues are very efficient, dequeues take $\Omega(p)$ steps to look at all $p$ lists
and return an item with the oldest timestamp.
(Items added by concurrent enqueues may get the same timestamp.)
Moreover, concurrent dequeues may compete to claim the same item using a CAS, resulting
in a CAS retry problem.
